Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards

### 2024-06-25 article.tex
abstract

The assessment of environmental sustainability in the Australian winegrowing industry remains a complex issue involving changing and compounding factors. To address this, we developed a Bayesian Network (BN) using data and expert elicitation to summarise the key factors, their relationships, and how they come together to influence vineyards' environmental outcomes. The study leveraged diverse expert perspectives to mitigate biases in probability estimations and promote discourse.

The development of the BN involved an iterative process, including variable selection and definition, the defining of model structure and variable relationships, and finally the determining of relationship significance through probabilities. Expert input was pivotal in structuring the BN model, ensuring relevance to industry, and how a variables influence changed across regions and scenarios.

Due to the possible variation in any given vineyard scenario the BN model was expanded to review a case study of the Coonawarra wine region in South Australia. This highlighted regional differences between growers whilst also maintaining the significance of industry-wide concerns such as the use of agrochemicals. To promote accessibility and scrutiny the BN was further developed into an application, allowing the possibility of further industry and stakeholder feedback; enabling a systematic re-evaluation of significant factors to the wine growing industry and how they change over time.

@@

>>>>

Environmental sustainability in the Australian winegrowing industry involves complex, interacting factors. To address this, we developed a Bayesian Network (BN) model, integrating data and expert input to summarise key factors, their relationships, and impacts on vineyard outcomes. The BN model was iteratively refined, involving variable selection, structure definition, and probability estimation, with expert input ensuring industry relevance and regional adaptability. A case study of the Coonawarra region highlighted regional differences while underscoring industry-wide concerns, such as agrochemical use. The BN model, accessible via an application, allows for continuous industry feedback and adaptation. Future research should explore dynamic BNs to address temporal variations and extend applicability to other regions. This study underscores the potential of BNs as powerful tools for sustainability analysis in agriculture, offering valuable insights for sustainable vineyard management.

@@

% end
